---
title: "R studio learning"
author: "adfghk"
output: 
  html_document:
    toc: TRUE
    theme: united
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

##1.Introduce to R Progamming
###What is statistical programming?

Computer programming involves controlling computers,telling them what calculations to do,what to display,etc.
One definition might be that it is the kind of computer programming statisticians do-but statisticians do all sors of porgramming.Another would be that it is kind of programming one does when one is doing statistics-but again,satistics involves a wide variety of computing tasks.
Statistical programming involves doing computations to aid in statistical analysis.

###Starting and quitting R
The greater than sign(>)is the prompt symbol.When this appears,you can begin typing commands.
We can type simple arithmetical expression at the >prompt.
```{r}
5+49
```

the [1] indicates that this is the first result from the command.Other commands returns multiple values,and each line of results will be labeled to aid the user in deciphering the output.


Take a command for example.
```{r}
options(width=40)
1:20
```

Here are some additinal examples for calculator.
```{r,eval=FALSE}
3*5
3-8
12/4
```

If you want to quit your R session,type
```{r,eval=FALSE}
q()
```

##2.Basic features of R
### Calculating with R

We saw in the previous section that it can be used to do scalar arithmetic.
```{r}
3 ^ 4
31 %% 7
31 %/% 7
7*4+3
```




### Named storage
(設未知數的概念)

For example,suppose we would like to store  the result of the calculation 1.0025^30 for future use.We will assign this value to an object called _interest.30_.To this,we type
```{r}
interest.30 <- 1.0023^30
```
We tell R to make the assignment using an arrow that points to the left.

We can see the results of this assignment by typing the name of our new object at the prompt:
```{r}
interest.30
```

Take other examples of named storage.

Example1

```{r}
intRate <- 0.01
n <- 10
principal <- 1500
payment <- principal * intRate / (1-(1+intRate)^(-n))
payment
```

Example2

Consider the standard formula for the sample variance of the sample x1,...,xn:

$S^2$=$\frac{1}{n-1}$ $\sum_{i=0}^{n}$ $(x{i}-\overline{x})^2$

where $\overline{x}$ is the sample mean,$\frac{1}{n}$ $\sum_{i=0}^n$ $xi$.  
In R,$S^2$ is avaliable as var(),and $\overline{x}$ is mean().For example:
```{r}
x <- 1:11
mean(x)
var(x)
sum((x-mean(x))^2)/10
```





###Vectors

A numeric vector is a list of numbers.

The c() function is used to collect things together into the vector.We can type
```{r}
c(0,7,8)
```

Also,we can assign this to a named object
```{r}
x<- c(0,7,8)
x
```


```{r}
numbers5to20 <- 5:20
numbers5to20
```


Vectors can be join together.
```{r}
c(numbers5to20,x)
```


There are some other examples:
```{r}
number100to200<- 100:200
number100to200[22]

number100to200[c(1:10,30:40)]
```



###Simple patterned vectors

Patterned vectors can also be produced using the seq() function as well as the rep() function.

Consider the following example:
```{r}
rep(3,12)  #repeat the value3 for 12 times
rep(seq(2,20,by=2),2) #repeat the pattrn 2 4....20,twice
rep(c(1,4),c(3,2)) #repeat 1,3 times and 4,twice
rep(c(1,4),each=3) #repeat each value 3 times
rep(seq(2,20,2),rep(2,10)) #repeat each value twice
rep(c(2,3,4),each=3)
rep(10,5)
rep(seq(11,30,by=3),3)
rep(c(2,3,4),each=3)
rep(seq(11,30,by=3),rep(3,7))#想成線代:seq(11,30,by=3)x(3,3,3,3,3,3,3)
rep(seq(11,30,by=3),rep(5,7))


rep(seq(11,30,by=3),c(rep(3,3),rep(4,4)))

rep(seq(11,30,by=3),c(3,3,3,4,4,4,4))

rep(c(11,14,17,20,23,26,29),c(3,3,3,4,4,4,4))
```

###Missing value and other special value

The missing value symbol is NA.Missing value often arise in real data problems,but they can also arise because of the way calculations are performed.

```{r}
some.evens<- NULL #create a vector with no elements
some.evens[seq(2,20,2)] <- seq(2,20,2)
some.evens
```


Take x for example.

```{r}
x=c(0,10,20)
x[-3]
x[-1]
x[-c(1,2)]
x[0]
x[c(0,2)]
x-NULL
x[seq(2,20,2)]=seq(1,20,2)
x
x=c(0,10,20)
x/x
1/x
x[0.4]
x[0.99]
x[1.1]
```

###Character vectors

Scalars and vectors can be made up of strings of characters instead of numbers.

For example,
```{r}
colors=c("brown","yellow","blue")
more.colors=c(colors,"green","magenta","cyan") #append some new elements to colors

z=c("brown","yellow",1)
z
more.colors
```

There are two operations you might perform.


substr() is the former takes argument substr(x,start,stop),where x is the vector of charater strings,and _start_
and _stop_ say which character to keep.
```{r}
substr(colors,2,3)
```


The other basic operation is building up strings by concatenation.Use the paste() function for this.For example:

```{r}
paste(colors,"candy")

paste0(colors,"candy")

paste0(colors,"-","candy")

paste(colors,c(colors,"red"))

paste(colors,c(colors,"red"),sep=" ")

paste(colors,c(colors,"red"),sep=":")

paste("several",colors,"s",sep="")

paste("I like",colors,collapse=",")
```

###Factors

Factors offer an alternative way of storing character data.

For example,
```{r}
fac=c("A","B","A","B")
fac

fac=factor(fac)
fac

as.factor(fac)
```



```{r}
fac2=c("AAAAAAAAAA","ABABABABAB","AAAAAAAAAA","ABABABABAB",1111)
fac2

fac2=factor(fac2)
fac2

as.integer(fac2)
```


```{r}
fac3=fac2[-5]
fac3
as.integer(fac3)
```


The labels for the labels are only stored once each,rather than being repeated.The codes are indices into the vector of levels:

```{r}
grp <- c("control","treatment","control","treatment")
grp

grp <- factor(grp)
grp

as.integer(grp)

levels(grp)

levels(grp)[as.integer(grp)]
```


###More on exacting elements from vectors

As for numeric vectors,square brackets[] are used to index factor and character vector elements.

For example,grp has four elements,so we can print out the third element by typing
```{r}
grp[3]
more.colors[2:5]
```

When there may be missing valus,tje is.na() function should be used to detect them.
```{r}
is.na(some.evens)
```

We can located the non-missing values in some.evens as follows:
```{r}
!is.na(some.evens)
```

We can then display the even numbers only:
```{r}
some.evens[!is.na(some.evens)]
```


###Matrix and arrays

To arrange values into the matrix

```{r}
m2 <- matrix(1:6,nrow=2,ncol=3)
m2

m2[1,2] #the value in first row and second column

m2[4]

m2[1,]

m2[,1]
```

A more way to store data is in the _array_. Arrays have multiple indices.
```{r}
a <- array(1:24,c(3,4,2))
a
```

Example3
```{r}

color=c("red","red","red1","blue")
number=c(1,3,5,7)
logic=c(T,T,F,F)

out.fr=data.frame(colors=color,numbers=number,logics=logic)
#每一行可以存不同格式的資料
out.fr


out.fr=data.frame(color,number,logics=logic)
out.fr

out.fr

out.fr[ ,2] #call by position
out.fr[ ,"number"] #call by name
out.fr$number #call by name

2*out.fr #文字不能存 邏輯值可以存，直接乘
class(out.fr)
class(m2)
class(out.fr$color)
class(color)


out.fr["number"]

class(out.fr[ ,"number"])
class(out.fr["number"])
```

###Built in graphics functions 

Two basic plots are the histogram and the scatterplot.

(1)Histogram
```{r}
x<-c(12,15,13,20,14,16,10,10,8,15)
hist(x)
```

(2)Scatterplot
```{r}
x <- seq(1,10)
y <- x^2-10*x
plot(x,y)
```

(3)A simple example involves plotting the sine function on the interval [0,6pi]:
```{r}
curve(expr=sin,from=0,to=6*pi)
```
The expr parameter is either a function or an expression in terms of x.

(4)
```{r}
curve(x^2-10*x,from=1,to=10)
```

###Logical vectors and relational operators

We have used the c() function to put numeric vectors together as well as character vectors.

```{r}
a=c(TRUE,FALSE,FALSE,TRUE)
b=c(13,7,8,2)
b[a]
sum(a)
```

If we attempt logical operations on a numerical vector,0 is taken to be FALSE,and any nonzero value is taken to be TRUE
```{r}
!a
```

Example4
```{r}
a=c(3,5,7)
b=c(1,5,8)
a[a>b]
```

###Data input and output

When in an R session,it is possible to read and write data to files outside of R.


Example5
```{r}
x=c(1:100,201:300)
hist.x=hist(x)
```

Use the setwd() function,and all data input and output will default to the mydata folder in the D:drive.
```{r,eval=FALSE}
setwd("D:/mydata")
```

In order to save a object for a future session type:
```{r,eval=FALSE}
dump("hist.x","hist.x.R") 
```

To retrieve the vector in a future session,type:
```{r,eval=FALSE}
source("hist.x.R")
```

To save all the objects that you have crated during a session,type:
```{r,eval=FALSE}
dump(list=objects(),"all.R")
```

 
 
 
###Redicting R output

Output can be directed to a file with the sink() function.

For example,consider the greenhouse data in the vector solar.radiation,type:
```{r,eval=FALSE}
sink("solarmean.txt") #create a file solarmean.txt for output
mean(solar.radiation) #write mean value of it
sink() #close solarmean.txt,print new output
```



Example6
```{r}
sink("try2.txt")
y=1:10
x=sin(y)
sink()
```


###Saving and retrieving image files

If R is started in another directory,the load() function may be used to load the workspce image.
It is possible to save workspce images without quitting.
For example,
```{r.eval=FALSE}
save.image("temp.RData")
load("temp.RData")
```


###Data frames and the read.table function

Data sets frequently consist of more than one column represents measurements of a single variable.Each row usually represents a single observation.

If such a data set is stored in a file,then it can be read into an R data frame.Typing:
```{r,eval=FALSE}
pretend.df=read.table("D:/pretend.dat",header=F)
pretend.df
```

```{r,eval=FALSE}
pretend.df=read.table("D:/pretend.dat",header=T)
pretend.df$z
```

###Lists

Example7
```{r}
x <- c(3,2,3)
y <- c(7,7)
list(x=x,y=y)
x
y
```

##3.Progamming statistical graphics



```{r}
VADeaths
```


(1)bar charts
the beside=TRUE argument causes the values in each column to be plotted side by side
legend=TRUE causes the legend in the top right to be added.
ylime=c(0,90) argument modifies the vertical scale of the graph to make room for the legend.
```{r}
barplot(VADeaths,beside=TRUE,legend=TRUE,ylim=c(0,90),
 ylab="Deaths per 1000",
 main="Death rates in Virginia")
```


(2)dot charts

```{r}
dotchart(VADeaths,xlim=c(0,75),
 xlab="Death per 1000",
 main="Death rates in Virginia")
```


(3)pie charts
```{r}
groupsizes<- c(18,30,32,10,10)
labels<-c("A","B","C","D","F")
pie(groupsizes,labels,col=c("grey40","white","grey","black","grey90"))
```


(4)histograms

a.
```{r}
x<-rnorm(100)
hist(x)
```

b.
```{r}
hist(x,breaks=5)
```

c.
```{r}
hist(x,10)

hist(x,breaks=10)
```


(5)box plots

a.
```{r}
boxplot(Sepal.Length ~ Species , data=iris,
 yab="Sepal length(cm)",main="Iris measurements",
 boxwex=0.5)
```


b.
```{r}
boxplot(Sepal.Length ~ Species,data=iris,
 yab="Sepal length(cm)",main="Iris measurements",
 boxwex=0.1)
```


(6)scatter plots

```{r}
x<-rnorm(100) #assign 100 random normal observations to x
y<-rpois(100,30) #assign 100 random poisson observations to y,mean value is 30
mean(y) #the resulting value should be near 30
plot(x,y,main="Poisson versus Normal")

#other try
plot(x,y) #plots a broken line
plot(sort(x),sort(y)) #a plot of the sample "quentiles"

```


(7)qqplots

```{r}
X<-rnorm(1000)

A<-rnorm(1000)
qqplot(X,A,main="A and X are the same")

B<- rnorm(1000,mean=3,sd=2)
qqplot(X,B,main="B is rescaled X")

C<-rt(1000,df=2)
qqplot(X,C,main="D is skewed to the right")


D<-exp(rnorm(2000))
qqplot(X,D,main="D is sknewed to the right")

```


###Adding to plots
程式碼                         |功能
-------------------------------|--------------------------------
`points(x,y,...)`              |  
`lines(x,y,...)`               |adds lines segments  
`text(x,y,labels,..)`          |adds text into the graph
`obline(a,b,...)`              |adds the line y=a+bx
`abline(h=y,...)`              |adds a horizontal line
`abline(v=x,...)`              |adds a vertical lines 
`polygon(x, y, ...)`           |adds a closed and possibly filled polygon
`segments(x0, y0, x1, y1, ...)`| draws line segments
`arrows(x0, y0, x1, y1, ...)`  |draws arrows
`symbols(x, y, ...)`           |draws circles, squares, thermometers, etc.
`legend(x, y, legend, ...)`    |draws a legend.


**Example8**  
We will use measurements which are stored in a data frame called indexfinger.
```{r,eval=FALSE}
indexfinger=read.table("d:/indexfinger.txt",header=r)
```

Then we can create a simple scatter plot.
```{r,eval=FALSE}
plot(width~length,data=indexfinger)
```

Suppose that after plotting this figure, we decide to highlight the male
and female with the longest fingers.  
We will use the
points() function to plot additional points on the graph on top of the
original ones with the following code
```{r,eval=FALSE}
with(indexfinger[c(3, 7),], points(length, width, pch=16)) #the pch=16 argument changes the plotting character from the default open circle to a solid black dot.
```

Another possibility would be to specify the pch value in the original
call to plot()
````{r,eval=FALSE}
plot(width ˜ length, pch=as.character(sex), data=indexfinger)
```

We could then add linear regression lines for the males and the females,
and a legend to identify them.
```{r,eval=FALSE}
abline(lm(width ˜ length, data=indexfinger, subset=sex=="M"), lty=1)
abline(lm(width ˜ length, data=indexfinger, subset=sex=="F"), lty=2)
legend("topleft", legend=c("Male", "Female"), lty=1:2)
```


####One may also wish to annotate graphs outside the plot region.  
Several functions exist to do this:

程式碼                             |功能
-----------------------------------|-----------------------------------
`title(main, sub, xlab, ylab, ...)`|adds a main title, a subtitle, an x-axis label and/or a y-axis label
`mtext(text, side, line, ...)`     |draws text in the margins
`axis(side, at, labels, ...)`      |adds an axis to the plot
`box(...)`                         | adds a box around the plot region.


**Example9**
```{r}
par(mar=c(5, 5, 5, 5) + 0.1)
plot(c(1, 9), c(0, 50), type="n", xlab="", ylab="")
text(6, 40, "Plot region")
points(6, 20)
text(6, 20, "(6, 20)", adj=c(0.5, 2))
mtext(paste("Margin", 1:4), side=1:4, line=3)
mtext(paste("Line", 0:4), side=1, line=0:4, at=3, cex=0.6)
mtext(paste("Line", 0:4), side=2, line=0:4, at=15, cex=0.6)
mtext(paste("Line", 0:4), side=3, line=0:4, at=3, cex=0.6)
mtext(paste("Line", 0:4), side=4, line=0:4, at=15, cex=0.6)
```

###Setting graphical parameter

After a device is opened, other graphical parameters may be set using
the par(...) function.  
This function controls a very large number of parameters.For example,

程式碼                             |功能
-----------------------------------|---------------------------------
`mfrow=c(m, n)`                    |tells R to draw m rows and n columns of plots, rather than going to a new page for each plot.
`mfg=c(i, j)`                      |says to draw the figure in row i and column j next.
`ask=TRUE`                         | tells R to ask the user before erasing a plot to draw a new one.
`cex=1.5`                          |tells R to expand characters by this amount in the plot region.
`mar=c(side1, side2, side3, side4)`| sets the margins of the plot to the given numbers of lines of text on each side.
`oma=c(side1, side2, side3, side4)`|sets the outer margins.
`usr=c(x1, x2, y1, y2)`            | sets the coordinate system within the plot with x and y coordinates on the given ranges.


The par() function is set up to take arguments in several forms.  
If you give character strings (e.g. par("mfrow")), the function will return the
current value of the graphical parameter.  
If you provide named arguments,you will set the corresponding parameter,and the previous value will be returned in a list.  
Finally, you can use a list as input to set several parameters at once.



##4.Programming with R

###The **for()** loop

The for() statement allows one to specify that a certain operation should be repeated a fixed number of times.

For example,
```{r}
Fibonacci <- numeric(12)
Fibonacci[1] <- Fibonacci[2] <- 1
for (i in 3:12) Fibonacci[i] <- Fibonacci[i - 2] + Fibonacci[i - 1]
Fibonacci
```


###The if() statement

The if()statement allows us to control which
statements are executed, and sometimes this is more convenient.

```{r}
x=3
if(x>2) y=x^2 else y=cos(x)
y

x=1
if(x>2) y=x^2 else y=cos(x)
y

x=1
if(x==2) y=x^2 else y=cos(x)
y

x=1
if(x!=2) y=x^2 else y=cos(x)
y
```


**Example10**
```{r}

corplot <- function(x,y,plotit) {
 if(plotit==TRUE) plot(x,y)
 cor(x,y)
}
```

```{r}
corplot(c(1,3,5,7),c(2,2,10,2),F)
```

```{r}
corplot(c(1,3,5,7),c(2,2,10,2),T)
```


**Example11**
```{r}
Eratosthenes <- function(n) {
  #Return all prime numbers up to n (based on the sieve of Eratosthenes)
  if (n >=2) {
    sieve <- seq(2,n)
    primes <- c()
    for (i in seq(2,n)) {
      if (any(sieve==i)) {
        primes <- c(primes,i)
        sieve <- c(sieve[(sieve%%i)!=0],i)
      }
    }
    return(primes)
  } else {
      stop("Input value of n should be at least 2.")
  }
}
```

###The while() loop


**Example12**
```{r}
Fib1 <- 1
Fib2 <- 1
Fibonacci <- c(Fib1,Fib2)
while (Fib2<300) {
	Fibonacci <- c(Fibonacci,Fib2)
	oldFib2 <- Fib2
	Fib2 <- Fib1+Fib2
	Fib1 <- oldFib2
}
```


**Example13**
```{r}
Fib1 <- 1
Fib2 <- 1
Fibonacci <- c(Fib1,Fib2)
while (Fib2<300) {
	Fibonacci <- c(Fibonacci,Fib2)
	n=length(Fibonacci)
	Fib2=Fibonacci[n-1]+Fibonacci[n]
}
Fibonacci
```


**Example14**
```{r}
Fibonacci <- c(1,1)
while (Fibonacci[length(Fibonacci)]+Fibonacci[length(Fibonacci)-1]<300) {
	Fibonacci <- c(Fibonacci,Fibonacci[length(Fibonacci)-1]+Fibonacci[length(Fibonacci)])
}
Fibonacci
```





###Using fix()

Sometimes we make errors when we write functions.To help us replace the
incorrect version with a new one, the fix()function can be used to make
corrections.  
fix()can also be used to create functions.

###Documentation using  "#"

The "#" symbol is a simple way of inserting comments such as titles and descriptions into R functions and scripts.  
R ignores all text from the "#" character to the end of the line.

###Some other function to use

(1)
>sort()

We might use sort() to sorting the vector consisting of some elements.For example,
```{r}
x<- c(3,5,24,6,2,4,13,1)
sort(x)
sort(c(2,1))
sort(c(2,24,3,4,5,13,6,1))
```


**Example15**
```{r}
sort1 <- function(x) {
  # x is initially the input vector and will be modified to form the output
  # first is compared with last
  for (last in length(x):2) {
    for (first in 1: (last-1)) {
      if (x[first] > x[first + 1]) {
        save <- x[first]
        x[first] <- x[first + 1]
        x[first + 1] <- save
      }
    }
  }
  return(x)
}
sort(1)
```


**Example16**
```{r}
mergesort = function(x) {
  #Check for a vector that doesn't need sorting
  len = length(x)
  if (len < 2) result = x
  else {
    #2: sort x into result
    #2.1: split x in half
    y = x[1:(len/2)]
    z = x[(len/2+1):len]
    #2.2: sort y and z
    y = mergesort(y)
    z = mergesort(z)
    #2.3: merge y and z into a sorted result
    result=c()
    #2.3.1: while (some are left in both piles)
    while (min(length(y), length(z)) > 0) {
      #2.3.2: put the smallest first element on the end
      #2.3.3: remove it from y or z
      if (y[1] < z[1]) {
        result = c(result, y[1])
        y = y[-1]
      } else {
        result = c(result, z[1])
        z= z[-1]
      }
    }
    #2.3.4: put the leftovers onto the end of result
    if(length(y) >0) {
      result = c(result,y)
    } else {
      result = c(result,z)
    }
  }
  return(result)
}

mergesort(c(1,5,3,4))
```


(2)
>traceback()

In R, you can obtain extra information about an error message using the traceback() function.  
When an error occurs, R saves information about the current stack of active functions, and traceback() prints this list.

For example,
```{r,eval=FALSE}
cv <- function(x) {
+ sd(x / mean(x))
+ }
cv(0)
```
Error in var(x, na.rm = na.rm) : missing observations in cov/cor  
The error message talks about the function var(), which we didn’t use.  
To find out where it was called from, we use traceback():
```{r,eval=FALSE}
traceback()
```



(3) 
>browser()

Rather than using cat() or print() for debugging, R allows you to call the function browser().  
This will pause execution of your function, and allow you to examine (or change!) local variables, or execute any other R command, inside the evaluation environment of the function.  
You can also execute a debugger command:

command          |function
-----------------|-----------------
n – “next”       |execute the next line of code, single-stepping through the function
c – “continue”   |let the function continue running
Q –              |quit the debugger.

--------------------------------------------------

(4)
>debug()

Another way to enter the browser is to use the debug() function.You mark function f for debugging using debug(f), and then the browser will be called when you enter the function.  
Turn off debugging using undebug(f).


###Learning your tools

R is designed to work with vectors.  
Operations on whole vectors are usually much faster than working one element at a time.  
Summing two vectors could be done as follows:
```{r}
X = rnorm(100000) # Xi ~ N(0,1) i=1,...,100000
Y = rnorm(100000) # Yi ~ N(0,1) i=1,...,100000
Z = c()

for (i in 1:100000) {
  Z = c(Z, X[i] + Y[i]) # this take about 25 seconds
}
```

However, this is extremely inefficient in R. First, it reallocates the vector Z 100 000 times, increasing its length by one each time.   
Since we know the length of Z in advance, we could allocate it once, and modify its entries:
```{r}
Z = rep(NA, 100000)
for (i in 1:100000) {
  Z[i] = X[i] + Y[i] # this take about 0.88 seconds
}
Z=X+Y
```


##5.Simulation


###Some command of the random variables of distributions


####Uniform random variable

(1)
>runif(n, min = a, max = b)


Execution of this command produces n pseudorandom uniform numbers on the interval [a, b].   
The default values are a = 0 and b = 1. The seed is selected internally.

For example,
```{r}
runif(5)
runif(10,min=-3,max=10)
```


---------------------------------------------------------

(2)
>set.seed()

This would be useful when debugging a program that uses random numbers, or in other situations where repeatability is needed.

For example,
```{r}
set.seed(32789)  # this ensures that your output will match ours
runif(5)

set.seed(100)
runif(10,min=-3,max=10)

set.seed(100)
runif(10,min=-3,max=10)

set.seed(100)
runif(10,min=-3,max=10)
```


**Example17**
```{r}
set.seed(23207) # use this to obtain our output
guesses <- runif(20)
correct.answers <- (guesses < 0.2)
correct.answers
```


The total number of correct guesses and incorrect guesses canbe calculate:
```{r}
table(correct.answers)
```

**Example18**
```{r}
round(1.123,2)

u2 <- runif(1000)
u1 <- runif(1000)
X <- u1+u2
Y <- u1-u2
plot(Y ~ X)
```

```{r}
cor(X,Y)
```

```{r}
u2 <- runif(1000)
u1 <- runif(1000)
cor(u1,u2)
```

------------------------------------------

####Binomial random variable

(3)
>dbinom(x, size, prob)

Here, size and prob are the binomial parametersmand p, respectively,while x denotes the number of “successes.”  
The output from this function is the value of P(X = x).

For example,
```{r}
dbinom(x = 4, size = 6, prob = 0.5)
```

Thus, P(X = 4) = 0.234, when X is a binomial random variable with m = 6 and p = 0.5.

-----------------------------


(4)
>pbinom():Cumulative probabilities of the form P(X<=x)  
>qbinom():Gives the quentilies for the binomial distribution.


```{r}
pbinom(4, 6, 0.5)
qbinom(0.89, 6, 0.5)
```

------------------------------

(5)
>rbinom(n, size, prob)

Here, size and prob are the binomial parameters, while n is the
number of variates generated.  

For example:
```{r}
defectives <- rbinom(24, 15, 0.1)
defectives
any(defectives>5)
```
   
**Example19**   
Simulate 10000 binomial pseudorandim numbers with parameters 20 and 0.3,assigning them to a vector called binsim.  
Let X be a binomial (20.03) random variable.  
Use the simulated numbers to estimate the following

```{r}
binsim <- rbinom(10000,20,0.3)
#(a)P(X<=5) #usepbinim
sum(binsim <= 5)/10000

pbinom(5,20,0.3) #pbinom(x,size,prob)
#(b)P(X=5) #use dbinom
sum(binsim =5)/10000

dbinom(5,20,0.3)

#(c)E[X]
mean(binsim)

true_mean <- 20*0.3
true_mean

#(d)Var(X)
var(binsim)


true_var <- 20*0.3*0.7
#(e)the 95th percentile of X(use quantile() function)
quantile(binsim,0.95)


qbinom(0.95,20,0.3) #機率p對應之分位數

#(f)the 99th percentile of X
quantile(binsim,0.99)

qbinom(0.99,20,0.3)

#(g)the 99.9999th quantile of X
quantile(binsim,0.999999)

qbinom(0.999999,20,0.3)
#need a large amount of pseudorandom numbers to estimate the exstreme quantiles accurately
```

----------------------------


####Poisson random variable


(6)
>dpois(x, lambda)

Here, lambda is the Poisson rate parameter, while x is the number of Poisson events.  
The output from the function is the value of P(X = x).

For example:

```{r}
dpois(x = 3, lambda = 0.5)
```

Therefore, P(X = 3) = 0.0126, if X is Poisson random variable with mean 0.5.

------------------------------

(7)
>rpois(n, lambda)

The parameter n is the number of variates produced, and lambda is as above.  

For example:
```{r}
rpois(10, 3.7)
```

-------------------------------


####Exponential random variable


(8)
>pexp(q, rate)

The output from this is the value of P(T ≤ q), where T is an exponential random variable with parameter rate.

For example:
```{r}
pexp(1, rate = 3)
```

Thus, P(X ≤ 1) = 0.95, when X is an exponential random variable with a rate of 3.

-------------------------

(9)
>rexp(n, rate)

The R function rexp() can be used to generate n random exponential variates.

For example:
```{r}
X <- rexp(25, rate = 1.5)
cumsum(x)
```

------------------------

####Normal random variable

(10)
>dnorm() :The normal density function.  
pnorm() :The distribution function.  
qnorm() :The quantiles of the normal distribution.

For example,the 95th percentile of the normal distribution with a mean of 2.7 and a standard deviation of 3.3 is:
```{r}
qnorm(0.95, mean = 2.7, sd = 3.3)
```



(11)
>rnorm(n, mean, sd)

Normal pseudorandom variables can be generated using the rnorm() function in R.This produces n normal pseudorandom variates which have mean mean and standard deviation sd.

For example,we can simulate 10 independent normal variates with a mean of −3 and a standard deviation of 0.5 using:
```{r}
rnorm(10, -3, 0.5)
```

**Example20**  
Simulate x from the standard normal distribution, conditional on the event that 0 < x < 3. We will simulate from the entire normal distribution and then accept only those values which lie between 0 and 3.
```{r}
x <- rnorm(100000) # simulate from the standard normal
x <- x[(0 < x) & (x < 3)] # reject all x’s outside (0,3)
hist(x, probability=TRUE) # show the simulated values
```


###Monte Carlo integration

Suppose g(x) is any function that is integrable on the interval [a, b].  
The integral $\int_{a}^{b}$ $g(x)$   give the area of the region with a<x<b and y between 0 and g(x).  


**Example21**  

1.$\int_{0}^{\infty}$ $e^{-x^3}$

```{r}
set.seed(1)
x <- rexp(100000)
mean(exp(-x)^3/dexp(x))
```

2.$\int_{0}^{3}$ $sin(e^{x})$

```{r}
set.seed(1)
x<-runif(100000,min=0,max=3)
mean(sin(exp(x)))*3
```

3.$\int_{0}^{3}$ $\frac{1}{\sqrt{2\pi}}$ $e^{\frac{-x^2}{2}}$

```{r}
set.seed(1)
x<-runif(100000,min=0,max=3)
mean((1/sqrt(2*pi))*exp((-x^2)/2))*3
```


###Rejection sampling

We will show how to use rejection sampling to draw a random sample from a univariate density or probability function g(x), using a sequence of two examples

**Example22**

```{r}
k=0.45403
g=function(x)0.5*exp(-(x^1.5))/k
X<-rexp(100000)
W<-g(X)/dexp(X) #dexp:返回概率密度
mean<-weighted.mean(X,W) #weighted.mean 加權平均函數
mean
```


**Example23**

```{r}
kg=function(x)0.5*exp(-(x^1.5))
X=rexp(100000)
U=runif(100000)
# accept only those X
X=X[ U*dexp(X) < kg(X) ]
hist(X, freq = FALSE, breaks="Scott")
k=length(X) / 100000
g=function(x)kg(x) / k
curve(g, from=0, to=max(X), add=TRUE)
fbyk=function(x)dexp(x) / k
curve(fbyk, from=0, to=max(X), add=TRUE, lty=2)
```


##6.Computing linear algebra

Linear algebra deals with vector spaces and linear operations on them. In mathematics, we usually represent vectors as column vectors of numbers, and linear operations as matrices. 

###Constructing matrix objects

Syntax                       | function
-----------------------------|-----------------------------
matrix(data, nrow, ncol)     |data is a vector of nrow*ncol values
cbind(d1, d2, ..., dm)       |d1, ..., dm are vectors (columns)
rbind(d1, d2, ..., dn)       |d1, ..., dn are vectors (rows)


For example,
```{r}
H3 <- matrix(c(1, 1/2, 1/3, 1/2, 1/3, 1/4, 1/3, 1/4, 1/5), nrow=3)
H3
```

```{r}
cbind(seq(1, 3), seq(2, 4), seq(3, 5))
```

```{r}
1/cbind(seq(1, 3), seq(2, 4), seq(3, 5))
```



```{r}
matrix(seq(1, 12), nrow=3)
```

```{r}
x <- seq(1, 3)
x2 <- x^2
X <- cbind(x, x2)
X
```

```{r}
X<-matrix(c(1,2,3,1,4,9),ncol=2)
X
```

###Accessing matrix elements

**Example24**
```{r}
X[3,2]
X[3,]

X[3,,drop=FALSE]
X[,2,drop=FALSE]

colnames(X)

rownames(X)

rownames(X)<-c("obs1","obs2","obs3")
X
```


```{r,eval=FALSE}
X[,"x"]
```


###Matrix properties


The dimension of a matrix is its number of rows and its number of columns.  
The diagonal elements can be obtained using the diag() function.
```{r}
dim(X)

diag(X)

y=cbind(seq(1,3),seq(2,4),seq(3,5))
diag(y)
diag(diag(y))
diag(1:6)
```

The t() function is used to calculate the matrix transpose $X^T$ :
```{r}
t(X)
```


###Some apply of  matrix

upper triangular mayrix
```{r}
Hnew=H3=y
Hnew[upper.tri(H3,diag=TRUE)]<-0
Hnew
```


```{r}
x=matrix(1:6,nrow=3)
y=matrix(c(3,4,5,7,7,7),ncol=2)
x
y
```

```{r}
x*y
x%%y

solve(t(x)%*%y)
```


>solve() 

求逆矩陣(square matrix)

```{r}
set.seed(1)
z=matrix(rnorm(9),nrow=3)
z
solve(z) 
```

>crossprod()

The crossprod()function is a somewhat more efficient way to
calculate $Y^T$ $X$
```{r}
crossprod(y,x)
```


**Example25**
```{r}
x0=rep(1,6)
x1=10:15
A=cbind(x0,x1,x1^2,x1^3,x1^4,x1^5)
b=c(25,16,26,19,21,20)
out=solve(A,b)
names(out)=paste("a",0:5,sep="")
out
```

**Example26**
```{r}
X <- matrix(c(1, 2, 3, 1, 4, 9), ncol=2)
X_t <- t(X)
X_t_X <- X_t %*% X
X_inv <- solve(X_t_X)
H <- X %*% X_inv %*% X_t
H
```

>eigen()

Eigenvalues and eigenvectors can be computed using the function eigen().


```{r}
eigen(H)
eigen(H)$values #[1] 1.000000e+00 1.000000e+00 6.661338e-16
eigen(H)$vectors


trace=function(data) sum(diag(data))
trace(H)
sum(eigen(H)$values)
##the trace of the matrix H and the sum of the eigenvalues are the same

det(H)
prod(eigen(H)$values)
##they are close to zero
```

Definition: If H%*%x=a*x, then x is an eigenvector of H and a is an eigenvalue of H
```{r}
H%*%X[,1]
X[,1]
H%*%X[,2]
X[,2]
# Because H%*%X[,1]=1*X[,1], X[,1] is an eigenvector
# Because H%*%X[,2]=1*X[,2], X[,2] is an eigenvector

H%*%((diag(1,3)-H)[,1])
H%*%((diag(1,3)-H)[,2])
H%*%((diag(1,3)-H)[,3])
#H%*%((diag(1,3)-H)[,1])=0*(diag(1,3)-H)[,1], (diag(1,3)-H)[,1] is an eigenvector
#H%*%((diag(1,3)-H)[,2])=0*(diag(1,3)-H)[,2], (diag(1,3)-H)[,2] is an eigenvector
#H%*%((diag(1,3)-H)[,3])=0*(diag(1,3)-H)[,3], (diag(1,3)-H)[,3] is an eigenvector

H3=matrix(c(1,1/2,1/3,1/2,1/3,1/4,1/3,1/4,1/5),nrow=3)
```


>svd()

The singular value decomposition can be obtained using the function
svd(). 

```{r}
H3.svd <- svd(H3)
H3.svd
H3.svd$d
H3.svd$u
H3.svd$v
```

We can verify that these components can be multiplied in the appropriate way to reconstruct H3:
```{r}
H3.svd$u %*% diag(H3.svd$d) %*% t(H3.svd$v)
```

Because of the properties of the U, V and D matrices, the singular value decomposition provides a simple way to compute a matrix inverse.  

For example,$H_{3}^{-1}$= $V$ $D^{-1}$ $U^{T}$ can be recalculated as
```{r}
H3.svd$v %*% diag(1/H3.svd$d) %*% t(H3.svd$u)
```

>chol()

If a matrix A is positive definite, it possesses a square root. In fact, there are usually several matrices B such that $B^{2}$ =$A$.  
We can use chol() to find an _upper triangular matrix_ U such that $U^{T}$ $U$ = $A$.  

For example,
```{r}
H3.chol <- chol(H3)
H3.chol
crossprod(H3.chol, H3.chol)
```

>chol2inv()

Once the Choleski decomposition of a matrix $A$ = $U^{T}$ $U$ has been obtained, we can compute the inverse of A using the fact that $A^{−1}$ =$U^{−1}$ $U^{−T}$
```{r}
chol2inv(H3.chol)
```

>qr()  
qr.Q()  
qr.R()  


Another way of decomposing a matrix A is via the QR decomposition $A$ = $Q$ $R$, where Q is an orthogonal matrix, and R is an upper triangular matrix.  
This decomposition can be applied even if A is not square.  

To obtain the decomposition, we use the qr() function.    
The functionsqr.Q() and qr.R() can be applied to this object to obtain the explicit Q and R matrices. 


**Example26**
```{r}
H3.qr <- qr(H3)
H3.qr
H3.qr$qr
H3.qr$rank
H3.qr$qraux
H3.qr$pivot

Q <- qr.Q(H3.qr)
Q
R <- qr.R(H3.qr)
R
```

We can recover $H_3$ by multiplying Q by R:
```{r}
Q%*%R
```


>kappa()

The function kappa() can be used to compute the condition number of a given matrix (the ratio of the largest to smallest nonzero singular values).

```{r}
kappa(H3)
```


>outer()

The function outer() is sometimes useful in statistical calculations.  
It can be used to perform an operation on all possible pair of elements coming from two vectors.

```{r}
x1 <- seq(1, 5)
outer(x1, x1, "/")
```

Replacing the division operation with the subtraction operator gives all pairwise differences:
```{r}
outer(x1, x1, "-")
```

The third argument can be any function that takes two vector arguments.  
The second argument can differ from the first. 
```{r}
y <- seq(5, 10)
outer(x1, y, "+")
```

>apply()

It is sometimes necessary to apply the same function to each of the rows of a matrix, or to each of the columns.  
A for() loop could be used, but it is sometimes more efficient computationally to use the apply() function.

```{r}
apply(H3, 1, sum)
```

**Example27**
```{r}
apply(H3,1,function(x)sqrt(sum(x^2)))

x=cbind(x1=3,x2=c(4:1,2:5))
dimnames(x)[[1]]=letters[1:8]
apply(x,2,mean,trim=.2)

dimnames(x)

names(dimnames(x))=c("row","col")
```



##Numerical optimization

###The golden section search method

The golden section search method is a simple way of finding the minimizer of a single-variable function which has a singl minimum on the interval [a, b].  



**Example28**  

Consider minimizing the function $f(x)$ =$|x-3.5|$+ $(x-2)^{2}$ on the interval[0,5]
```{r}
f=function(x){
  abs(x-3.5)+(x-2)^2
}

curve(f,from=1,to=5)
```


**Example29**
```{r}
golden=function(f,a,b,tol=0.0000001){
  ratio=2/(sqrt(5)+1)
  x1=b-ratio*(b-a)
  x2=a+ratio*(b-a)
  
  f1=f(x1)
  f2=f(x2)
  
  while(abs(b-a)>tol) {
    if(f2>f1){
      b=x2
      x2=x1
      f2=f1
      x1=b-ratio*(b-a)
      f1=f(x1)
    } else{
      a=x1
      x1=x2
      f1=f2
      x2=a+ratio*(b-a)
      f2=f(x2)
    }
  }
  return((a+b)/2)
}


golden(f,1,5)
```


```{r}
section.s=function(f,a,b,tol=0.0000001,s=1/3){
  x2=b-s*(b-a)
  x1=a+s*(b-a)
  
  f1=f(x1)
  f2=f(x2)
  
  while(abs(b-a)>tol) {
    if(f2>f1){
      b=x2
    } else{
      a=x1
      x1=x2
      f1=f2
    }
    x2=b-s*(b-a)
    x1=a+s*(b-a)
    f1=f(x1)
    f2=f(x2)
    
    
  }
  return((a+b)/2)
}


section.s(f,1,5)
```


###Built in function

>optim(par, fn, ...)

The "par" parameter to optim() gives starting values for the parameters.  
Besides telling optim() where to begin, these indicate how many parameters will vary in its calls to fn, the second parameter.  
"fn" is an R function which evaluates the function to be minimized.  

Its first argument should be a vector of the same length as "par".optim() will call it repeatedly  

The optim() function has a number of optional parameters described on its help page. Besides those, the optional parameters in the ... list could include additional parameters to pass to "fn".

```{r}

f2=function(x)((x[1]-x[2])^2+(x[1]-2)^2+(x[2]-3)^4)/10

optim(c(1,1),f2)


f3=function(x){abs(x-3.5)+abs(x-2)+abs(x-1)}
optimize(f3,c(-10,10))
```


###Solving linear programming problems in R


There is more than one linear programming function available in R, but we believe the lp() function in the _lpSolve_ package may be the most stable version currently available.  



The lp() function has a number of parameters; the following are needed to solve minimization problems like the one in the earlier example:  

parameter        |function
-----------------|-----------------
objective.in –   |the vector of coefficients of the objective function
const.mat –      |a matrix containing the coefficients of the decision variables in the left hand side of the constraints; each row corresponds to a constraint
const.dir –      | a character vector indicating the direction of the constraint inequalities; some of the possible entries are >=, == and <=
const.rhs –      |a vector containing the constants given on the right-hand side of the constraints.

```{r}
library(lpSolve)

eg.lp=lp(objective.in=c(5,8),
         const.mat=matrix(c(1,1,1,2),nrow=2),
         const.rhs=c(2,3),const.dir=c(">=",">="))
eg.lp

eg.lp$solution
```


The lp() function can handle maximization problems with the use of the direction="max" parameter.  
Furthermore, the const.dir parameter allows for different types of inequalities.

**Example29**  

We will solve the problem:  
maxC = 5X1 + 8X2  
sunject to the constraints  
x1+x2 $\leq$ 2  
x1+2x2 = 3  
x1,x2 $\geq$ 0
```{r}
eg.lp=lp(objective.in=c(5, 8),
         const.mat=matrix(c(1, 1, 1, 2), nrow=2),
         const.rhs=c(2, 3),
         const.dir=c("<=", "="), direction="max")
eg.lp$solution
```












